Post MCMCglmm analyses

### 2021-04-26 Analysis/06-post_mcmcglmm_analyses.Rmd
plot.ellipses

@@

```{r}
## Loading the correct models
load("../Data/Processed/model_list.rda")
model_phylo1_clade3 <- model_list[[4]]
model_phylo4 <- model_list[[7]]
```

@@

```{r}
## Loading the data
load("../Data/Processed/morphdat.rda")
## Plotting it
colour_vector <- c("orange", "blue", "darkgreen")
plot(morphdat[, c(1,2)], pch = 19,
     col = colour_vector[morphdat$clade],
     xlab = "PC1 (90.5%)",
     ylab = "PC1 (6.86%)")
legend("topleft", legend = levels(morphdat$clade), col = colour_vector, pch = 19)
```

@@

```{r}
source("../Functions/plot.ellipses.R")
source("../Functions/get.covar.R")

## Selecting 100 random covariance matrices from the MCMCglmm
covar_matrices <- get.covar(model_phylo1_clade3,
                            n = 100,
                            simplify = FALSE)

## Plotting the results
plot(morphdat[, c(1,2)], pch = 19, cex = 0.5,
     col = colour_vector[morphdat$clade],
     xlab = "PC1 (90.5%)",
     ylab = "PC1 (6.86%)")
plot.ellipses(covar_matrices, centre = "none",
              col = c("grey",colour_vector),
              add = TRUE)
```

@@

```{r}
plot(morphdat[, c(1,2)], pch = 19, cex = 0.5,
     col = colour_vector[morphdat$clade],
     xlab = "PC1 (90.5%)",
     ylab = "PC1 (6.86%)")
plot.ellipses(covar_matrices, centre = "level",
              col = c("grey",colour_vector),
              add = TRUE)
```

>>>>

We can do all that with the internal package `"beer"` that can be install via github (if you have access to the repo):

```{r, eval = FALSE}
devtools::install_github("TGuillerme/elaboration_exploration_bird_beaks/beer")
```

```{r, eval = TRUE}
library(beer)
```

@@

```{r}
## Loading the correct models
data("model_list")
model_phylo1_clade3 <- model_list[[4]]
model_phylo4 <- model_list[[7]]
```

@@

```{r}
## Loading the data
data("morphdat")
## Plotting it
colour_vector <- c("orange", "blue", "darkgreen")
plot.space(morphdat,
           col = colour_vector,
           levels = morphdat$clade,
           xlab = "PC1 (90.5%)",
           ylab = "PC1 (6.86%)")
legend("topleft", legend = levels(morphdat$clade), col = colour_vector, pch = 19)
```

@@

```{r}
## Selecting 100 random covariance matrices from the MCMCglmm
covar_matrices <- get.covar(model_phylo1_clade3, n = 100)

## Plotting the results
plot.space(morphdat,
           col = colour_vector,
           levels = morphdat$clade,
           xlab = "PC1 (90.5%)",
           ylab = "PC1 (6.86%)")
plot.ellipses(covar_matrices, col = c("grey",colour_vector),
              add = TRUE)
```

@@

```{r}
plot.space(morphdat,
           col = colour_vector,
           levels = morphdat$clade,
           xlab = "PC1 (90.5%)",
           ylab = "PC1 (6.86%)")
plot.ellipses(covar_matrices, centre = mean,
              col = c("grey",colour_vector),
              add = TRUE)
```
